On the specific recursive structure of iterated parametricity

### 2025-09-28 paper/paper.tex
paper: strip itemize, wrap

The well-foundedness of the construction can be justified by the observation that:
\begin{itemize}
  \item Defining $\framep[n][p]$ for $p \leq n$ requires the definition
        of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
        dependency, as well as $\restrf[n][p-1]$, where
        $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its
        typing.

@@

        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                   \\
            \frametype[n][]           &                                              & \defeq & unit                                                                                         \\
            \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n][0,...,p-1] \times Type_l                                                       \\
            \\
            \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                   \\
            \paintingtype[n][]        & \star                                        & \defeq & unit                                                                                         \\
            \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
          \end{array}
        $$

        Formally, this can be described as:
        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \framep[n][0,...,p]        &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                          \end{array}\right)                                                  \\
                      \end{array}\right) : \frametype[n-1][0,...,p]
            }                                                                         \\
            \framep[n][0]              &
            \left(\begin{array}{l}
                      \star \\
                      \star \\
                      \star \\
                    \end{array}\right)     & \defeq & (\star,unit)                      \\
            \framep[n][0,...,p+1]      &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,p]   \\
                      \painting[n-1][0,...,p] \\
                      \restrf[n][0,...,p]     \\
                    \end{array}\right) & \defeq &
            \left(\begin{array}{l}
                      \framep[n][0,...,p]
                      \left(\begin{array}{l}
                          \framep[n-1][0,...,p-1]   \\
                          \painting[n-1][0,...,p-1] \\
                          \restrf[n][0,...,p-1]     \\
                        \end{array}\right)     ,                       \\
                      \Sigma d:\framep[n][0,...,p]
                      \left(\begin{array}{l}
                          \framep[n-1][0,...,p-1]   \\
                          \painting[n-1][0,...,p-1] \\
                          \restrf[n][0,...,p-1]     \\
                        \end{array}\right).\,                       \\
                      \quad \Pi\omega.\,\painting[n-1][p](\restrf[n][p](d)) \\
                    \end{array}\right) \\
            \restrftype[n][0,...,p-1]  &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                      \end{array}\right) : Type_{l}
            }                                                                         \\
            \restrftype[n][]           &
            \left(\begin{array}{l}
                      \star \\
                      \star \\
                    \end{array}\right)     & \defeq &
            unit                                                                      \\
            \restrftype[n][0,...,p]    &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,p]   \\
                      \painting[n-1][0,...,p] \\
                    \end{array}\right) & \defeq &
            \begin{array}{l}
              \Sigma \restrf[n][0,...,p-1]    \\
              \quad:\restrftype[n][0,...,p-1]
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]   \\
                        \painting[n-1][0,...,p-1] \\
                      \end{array}\right)
              .\,                             \\
              \Pi q\leq n.\,\Pi \omega.\,\framep[n][0,...,p]
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]   \\
                        \painting[n-1][0,...,p-1] \\
                        \restrf[n][0,...,p-1]     \\
                      \end{array}\right) \\
            \end{array}                             \\
          \end{array}
        $$
  \item Defining $\painting[n][p]$, in addition to the type dependency
        in $\framep[n][p]$, requires the definition of
        $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing
        dependency, as well as $\restrf[n][p-1]$. Since
        $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$,
        these dependencies are actually between $\painting[n][p,...,n]$,
        $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$,
        $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$. Also,
        for the case $p=n$, this also requires the assumption of an
        inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally,
        $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and
        $\restrf[n][p,...,n-1]$ respectively depend on the earlier
        values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and
        $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and
        dashed arrows for dependencies in subconstructions, here in the
        construction of $\framep$ at level $n-1$ and $\restrftype$ at
        level $n$:
        \begin{center}
          \fontsize{7.2}{9}\selectfont
          \begin{tikzcd}
            & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
            \udensdash{\framep}^{n,[0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
            \udensdash{\framep}^{n,[p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
            \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
            \painting[n-1][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
            \framep[n-1][0,...,p-1] &
            \udensdash{\restrf}^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
            \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
            \udensdash{\restrf}^{n,[p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
          \end{tikzcd}
        \end{center}

@@

        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \frametype[n][p,...,n]         &                                              & :      & Type_{l+1}                                                                                   \\
            \frametype[n][]                &                                              & \defeq & unit                                                                                         \\
            \frametype[n][p,...,n]         &                                              & \defeq & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
            \\
            \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :      & Type_{l+1}                                                                                   \\
            \paintingtype[n][]             & \star                                        & \defeq & unit                                                                                         \\
            \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
            \\
            \restrftype[n][p,...,n]        &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                          \end{array}\right)                                                  \\
                      \end{array}\right) : Type_{l}
            }                                                                                                                                                                                     \\
            \restrftype[n][]               &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,n-1]   \\
                      \painting[n-1][0,...,n-1] \\
                      \star                     \\
                      \star                     \\
                      \restrp[n][0,...,n-1]     \\
                    \end{array}\right)   & \defeq                                       & unit                                                                                                      \\
            \restrftype[n][p,...,n-1]      &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,p-1]   \\
                      \painting[n-1][0,...,p-1] \\
                      \framep[n-1][p,...,n-1]   \\
                      \painting[n-1][p,...,n-1] \\
                      \restrf[n][0,...,p-1]     \\
                    \end{array}\right)
                                           & \defeq                                       &
            \begin{array}{l}
              \framep[n][p]
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]   \\
                        \painting[n-1][0,...,p-1] \\
                        \restrf[n][0,...,p-1]     \\
                      \end{array}\right)
              \rightarrow \framep[n-1][p] \\
              \times                      \\
              \restrftype[n][p+1,...,n]
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p]       \\
                        \painting[n-1][0,...,p]     \\
                        \framep[n-1][p+1,...,n-1]   \\
                        \painting[n-1][p+1,...,n-1] \\
                        \restrf[n][0,...,p]         \\
                      \end{array}\right)
            \end{array}
          \end{array}
        $$

        This allows to define $\painting[n][p]$ formally:
        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \painting[n][p]              &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                          \end{array}\right)                                                  \\
                        \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                            \framep[n-1][p,...,n-2]   \\
                            \painting[n-1][p,...,n-2] \\
                            \restrf[n][0,...,p-1]     \\
                          \end{array}\right)                                                  \\
                        E:\framep[n-1][n-1]\rightarrow Type_l                                            \\
                      \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
            }                                                            \\
            \painting[n][n]              &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,n-1]   \\
                      \painting[n-1][0,...,n-1] \\
                      \star                     \\
                      \star                     \\
                      \restrp[n][0,...,n-1]     \\
                      \star                     \\
                      E                         \\
                    \end{array}\right) & \defeq & E                        \\
            \painting[n][p](p<n)         &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,p-1]   \\
                      \painting[n-1][0,...,p-1] \\
                      \framep[n-1][p,...,n-1]   \\
                      \painting[n-1][p,...,n-1] \\
                      \restrf[n][0,...,p-1]     \\
                      \restrf[n][p,...,n-1]     \\
                      E                         \\
                    \end{array}\right) & \defeq & d \mapsto
            \left(\begin{array}{l}
                      \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
                      \painting[n-1][0,...,p](\restrf[n][p](d))). \\
                      \painting[n][p+1,...,n-1]
                      \left(\begin{array}{l}
                          \framep[n-1][0,...,p]       \\
                          \painting[n-1][0,...,p]     \\
                          \framep[n-1][p+1,...,n-1]   \\
                          \painting[n-1][p+1,...,n-1] \\
                          \restrf[n][0,...,p]         \\
                          \restrf[n][p+1,...,n-1]     \\
                          E                           \\
                        \end{array}\right)(d,l)           \\
                    \end{array}\right) \\
          \end{array}
        $$

@@

\end{itemize}

\newpage
\bibliographystyle{msclike}
\bibliography{paper}

>>>>

The well-foundedness of the construction can be justified by the observation that:

Defining $\framep[n][p]$ for $p \leq n$ requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$, where $\restrf[n][p-1]$ in turn depends in $\framep[n][p-1]$ for its typing.

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                   \\
    \frametype[n][]           &                                              & \defeq & unit                                                                                         \\
    \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n][0,...,p-1] \times Type_l                                                       \\
    \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                   \\
    \paintingtype[n][]        & \star                                        & \defeq & unit                                                                                         \\
    \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
  \end{array}
\end{equation*}

Formally, this can be described as:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \framep[n][0,...,p]        &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                  \end{array}\right)                                                  \\
              \end{array}\right) : \frametype[n-1][0,...,p]
    }                                                                         \\
    \framep[n][0]              &
    \left(\begin{array}{l}
              \star \\
              \star \\
              \star \\
            \end{array}\right)     & \defeq & (\star,unit)                      \\
    \framep[n][0,...,p+1]      &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p]   \\
              \painting[n-1][0,...,p] \\
              \restrf[n][0,...,p]     \\
            \end{array}\right) & \defeq &
    \left(\begin{array}{l}
              \framep[n][0,...,p]
              \left(\begin{array}{l}
                  \framep[n-1][0,...,p-1]   \\
                  \painting[n-1][0,...,p-1] \\
                  \restrf[n][0,...,p-1]     \\
                \end{array}\right)     ,                       \\
              \Sigma d:\framep[n][0,...,p]
              \left(\begin{array}{l}
                  \framep[n-1][0,...,p-1]   \\
                  \painting[n-1][0,...,p-1] \\
                  \restrf[n][0,...,p-1]     \\
                \end{array}\right).\,                       \\
              \quad \Pi\omega.\,\painting[n-1][p](\restrf[n][p](d)) \\
            \end{array}\right) \\
    \restrftype[n][0,...,p-1]  &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
              \end{array}\right) : Type_{l}
    }                                                                         \\
    \restrftype[n][]           &
    \left(\begin{array}{l}
              \star \\
              \star \\
            \end{array}\right)     & \defeq &
    unit                                                                      \\
    \restrftype[n][0,...,p]    &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p]   \\
              \painting[n-1][0,...,p] \\
            \end{array}\right) & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][0,...,p-1]    \\
      \quad:\restrftype[n][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]   \\
                \painting[n-1][0,...,p-1] \\
              \end{array}\right)
      .\,                             \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n][0,...,p]
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]   \\
                \painting[n-1][0,...,p-1] \\
                \restrf[n][0,...,p-1]     \\
              \end{array}\right) \\
    \end{array}                             \\
  \end{array}
\end{equation*}

Defining $\painting[n][p]$, in addition to the type dependency in $\framep[n][p]$, requires the definition of $\painting[n-1][p-1]$, thus also $\framep[n-1][p-1]$ by typing dependency, as well as $\restrf[n][p-1]$. Since $\painting[n][p]$ also depends on $\painting[n][p+1]$ when $p<n$, these dependencies are actually between $\painting[n][p,...,n]$, $\painting[n-1][p,...,n-1]$, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n]$. Also, for the case $p=n$, this also requires the assumption of an inhabitant $X_{n}$ of $\nu$Set$^{=n}$. Finally, $\framep[n][p,...,n]$, $\framep[n-1][p,...,n-1]$ and $\restrf[n][p,...,n-1]$ respectively depend on the earlier values $\framep[n][0,...,p-1]$, $\framep[n-1][0,...,p-1]$ and $\restrf[n][0,...,p-1]$.  Below, we use dashed underline and dashed arrows for dependencies in subconstructions, here in the construction of $\framep$ at level $n-1$ and $\restrftype$ at level $n$:
\begin{center}
  \fontsize{7.2}{9}\selectfont
  \begin{tikzcd}
    & & \painting[n][p,...,n] \arrow[dd, bend right=70] \arrow[dddr] \arrow[d, dotted]\\
    \udensdash{\framep}^{n,[0,...,p-1]} \arrow[d, dashed] \arrow[ddr, dashed] & &
    \udensdash{\framep}^{n,[p,...,n]} \arrow[ll, dotted] \arrow[d, dashed] \arrow[ddr, dashed, shift right=2mm] \\
    \painting[n-1][0,...,p-1] \arrow[d, dotted] & &
    \painting[n-1][p,...,n-1] \arrow[ll, dotted] \arrow[d, dotted] \\
    \framep[n-1][0,...,p-1] &
    \udensdash{\restrf}^{n,[0,...,p-1]} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm, hook'] &
    \framep[n-1][p,...,n-1] \arrow[ll, dotted, bend left=15] &
    \udensdash{\restrf}^{n,[p,...,n-1]},X_n \arrow[ll, dotted, bend left=15] \arrow[l, dotted] \arrow[uul, dotted, hook']\\
  \end{tikzcd}
\end{center}

@@

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \frametype[n][p,...,n]         &                                              & :      & Type_{l+1}                                                                                   \\
    \frametype[n][]                &                                              & \defeq & unit                                                                                         \\
    \frametype[n][p,...,n]         &                                              & \defeq & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\
    \\
    \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :      & Type_{l+1}                                                                                   \\
    \paintingtype[n][]             & \star                                        & \defeq & unit                                                                                         \\
    \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\
    \\
    \restrftype[n][p,...,n]        &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                  \end{array}\right)                                                  \\
              \end{array}\right) : Type_{l}
    }                                                                                                                                                                                     \\
    \restrftype[n][]               &
    \left(\begin{array}{l}
              \framep[n-1][0,...,n-1]   \\
              \painting[n-1][0,...,n-1] \\
              \star                     \\
              \star                     \\
              \restrp[n][0,...,n-1]     \\
            \end{array}\right)   & \defeq                                       & unit                                                                                                      \\
    \restrftype[n][p,...,n-1]      &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p-1]   \\
              \painting[n-1][0,...,p-1] \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
              \restrf[n][0,...,p-1]     \\
            \end{array}\right)
                                   & \defeq                                       &
    \begin{array}{l}
      \framep[n][p]
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]   \\
                \painting[n-1][0,...,p-1] \\
                \restrf[n][0,...,p-1]     \\
              \end{array}\right)
      \rightarrow \framep[n-1][p] \\
      \times                      \\
      \restrftype[n][p+1,...,n]
      \left(\begin{array}{l}
                \framep[n-1][0,...,p]       \\
                \painting[n-1][0,...,p]     \\
                \framep[n-1][p+1,...,n-1]   \\
                \painting[n-1][p+1,...,n-1] \\
                \restrf[n][0,...,p]         \\
              \end{array}\right)
    \end{array}
  \end{array}
\end{equation*}

This allows to define $\painting[n][p]$ formally:
\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \painting[n][p]              &
    \multicolumn{3}{l}{
      \left(\begin{array}{l}
                \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                  \end{array}\right)                                                  \\
                \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                \left(\begin{array}{l}
                    \framep[n-1][0,...,p-1]   \\
                    \painting[n-1][0,...,p-1] \\
                    \framep[n-1][p,...,n-2]   \\
                    \painting[n-1][p,...,n-2] \\
                    \restrf[n][0,...,p-1]     \\
                  \end{array}\right)                                                  \\
                E:\framep[n-1][n-1]\rightarrow Type_l                                            \\
              \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
    }                                                            \\
    \painting[n][n]              &
    \left(\begin{array}{l}
              \framep[n-1][0,...,n-1]   \\
              \painting[n-1][0,...,n-1] \\
              \star                     \\
              \star                     \\
              \restrp[n][0,...,n-1]     \\
              \star                     \\
              E                         \\
            \end{array}\right) & \defeq & E                        \\
    \painting[n][p](p<n)         &
    \left(\begin{array}{l}
              \framep[n-1][0,...,p-1]   \\
              \painting[n-1][0,...,p-1] \\
              \framep[n-1][p,...,n-1]   \\
              \painting[n-1][p,...,n-1] \\
              \restrf[n][0,...,p-1]     \\
              \restrf[n][p,...,n-1]     \\
              E                         \\
            \end{array}\right) & \defeq & d \mapsto
    \left(\begin{array}{l}
              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
              \painting[n-1][0,...,p](\restrf[n][p](d))). \\
              \painting[n][p+1,...,n-1]
              \left(\begin{array}{l}
                  \framep[n-1][0,...,p]       \\
                  \painting[n-1][0,...,p]     \\
                  \framep[n-1][p+1,...,n-1]   \\
                  \painting[n-1][p+1,...,n-1] \\
                  \restrf[n][0,...,p]         \\
                  \restrf[n][p+1,...,n-1]     \\
                  E                           \\
                \end{array}\right)(d,l)           \\
            \end{array}\right) \\
  \end{array}
\end{equation*}

@@

\bibliographystyle{msclike}
\bibliography{paper}
